Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-21 paper/paper.tex
Fix issue with quality changed with time-to-close

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce increases the quality of a ticket;
  \item the presence of stack traces increases the quality of a ticket;
  \item the presence of attachments increases the quality of a ticket - more specifically tickets with screenshots, 
  config files or text files have lower times-to-complete than tickets without attachments;
  \item higher numbers of grammar errors impply lower quality scores for a ticket;
  \item higher sentiment scores imply higher quality scores for a ticket;
  \item higher numbers of words in comments imply lower quality scores for a ticket;
  \item higher number of words in description and summary imply lower quality scores for a ticket.
\end{itemize}

>>>>

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce reduces the time-to-close for a ticket;
  \item the presence of stack traces reduces the time-to-close for a ticket;
  \item the presence of attachments reduces the time-to-close for a ticket - more specifically tickets with screenshots, 
  config files or text files help tickets get closed quicker than those without attachments;
  \item higher numbers of grammar errors imply increased time-to-close values;
  \item higher sentiment scores imply reduced time-to-close values for a ticket;
  \item higher numbers of words in comments imply increased time-to-close values for a ticket;
  \item higher number of words in description and summary increase the time-to-close values for tickets.
\end{itemize}
